Final Report: Scenario 2 - MPX in the EU

### 2022-11-28 MS5.Rmd
Update to methods and insert of discussion section

To prepare this report, use data sets for the EU, explicitly including information on confirmed cases of MPX per country (euro_mpx_cases.csv) and census data (euro_census_stats.csv). The trajectory of this investigation incorporated four sets of data manipulation:
(1) Grouping countries into regions;
(2) Assessing necessary census information;
(3) Compiling data sets with confirmed case demographics;
(4) Creating tables and figures for visual analysis.
Countries were grouped by region based on a region's data set (world_country_regions.csv) to enhance the representation of positive cases per region. Within the euro_mpx_cases data set, relevant fields include country, country code, and confirmed cases. A curated demographic data set included information on age, sex, and the number of people per strata. 
As an aside with the census data, we chose to initially assess any "missing" data as "NA" when paired with a country. However then decided to print information with omit-NA's to allow aggregate fields to be added together for "Table 2: Population Demographic (Population Density) per Region."

>>>>

To prepare this report our team uses data sets for the EU, explicitly including information on confirmed cases of MPX per country (euro_mpx_cases.csv) and census data (euro_census_stats.csv). The trajectory of this investigation incorporated four sets of data manipulation:
(1) Grouping countries into regions;
(2) Assessing necessary census information;
(3) Compiling data sets with confirmed case demographics;
(4) Creating tables and figures for visual analysis.
Countries were grouped by region based on a region's data set (world_country_regions.csv) to enhance the representation of positive cases per region. Within the euro_mpx_cases data set, relevant fields include country, country code, and confirmed cases. A curated demographic data set included information on age, sex, and the number of people per strata. 
As an aside with the census data, we chose to initially assess any "missing" data as "NA" when paired with a country. However then decided to print information with omit-NA's to allow aggregate fields to be added together for "Table 2: Population Demographic (Population Density) per Region."
